Pattern matching for\\ $(231,213)$-avoiding permutations

### 2015-02-02 article.tex
Section 3

We need the following lemmata.

\begin{lemma}
\label{lemma:updown}
Let $\pi \in \AV_n(213,231)$.
For all $1 \leq i < j \leq n$, 
if $\stripe{\pi}{i}=\ustep$
and $\stripe{\pi}{j}=\dstep$
then $\pi(i)<\pi(j)$.
\end{lemma}

@@

		\begin{lemma}
		\label{lemma:upup}
		Let $\pi \in \AV_n(213,231)$,
		$\forall i,j \in [n]$, 
		$i<j$, 
		if $\stripe{\pi}{i}=\ustep$
		and $\stripe{\pi}{j}=\ustep$
		then $\pi(i)<\pi(j)$.
		\end{lemma}

		In other word, for every index $i$ and $j$ of an (231,213) avoiding permutation $\pi$,
		if $i$ is a ascent
		and $j$ is a ascent
		and $ i<j$
		then $p(i)<p(j)$.\\

@@

		\begin{lemma}
		\label{lemma:downdown}
 		Let $\pi \in \AV_n(213,231)$,
		$\forall i,j \in [n]$,
		$i<j$,
		if $\stripe{\pi}{i}=\dstep$
		and $\stripe{\pi}{j}=\dstep$
		then $\pi(i)>\pi(j)$.
		\end{lemma}

		In other word, for every index $i$ and $j$ of an (231,213) avoiding permutation $\pi$,
		if $i$ is a descent
		and $j$ is a descent
		and $ i<j$
		then $\pi(i)>\pi(j)$.\\

@@

>>>>

We need the following lemmata
(the proofs of Lemma~\ref{lemma:upup} and Lemma~\ref{lemma:downdown} 
are analogous and we omit them).

\begin{lemma}
	\label{lemma:updown}
	Let $\pi \in \AV_n(213,231)$.
	For all $1 \leq i < j \leq n$, 
	if $\stripe{\pi}{i}=\ustep$
	and $\stripe{\pi}{j}=\dstep$
	then $\pi[i] < \pi[j]$.
\end{lemma}

@@

\begin{lemma}
	\label{lemma:upup}
	Let $\pi \in \AV_n(213,231)$.
	For all $1 \leq i < j \leq n$,
	if $\stripe{\pi}{i}=\ustep$
	and $\stripe{\pi}{j}=\ustep$
	then $\pi[i] < \pi[j]$.
\end{lemma}

		% In other word, for every index $i$ and $j$ of an (231,213) avoiding permutation $\pi$,
		% if $i$ is a ascent
		% and $j$ is a ascent
		% and $ i<j$
		% then $p(i)<p(j)$.\\

@@

\begin{lemma}
	\label{lemma:downdown}
	Let $\pi \in \AV_n(213,231)$.
	For all $1 \leq i < j \leq n$,
	if $\stripe{\pi}{i} = \dstep$
	and $\stripe{\pi}{j} = \dstep$
	then $\pi[i] > \pi[j]$.
\end{lemma}

		% In other word, for every index $i$ and $j$ of an (231,213) avoiding permutation $\pi$,
		% if $i$ is a descent
		% and $j$ is a descent
		% and $ i<j$
		% then $\pi(i)>\pi(j)$.\\

@@

Most of the interest of the above lemmata stems from the following proposition.
